 \documentclass[letter,10pt]{letter}
\usepackage[utf8x]{inputenc}
\usepackage{hyperref}
\usepackage[margin=3cm]{geometry}

\signature{
Carlos Barreto\\
\mbox{Postdoctoral researcher} \\
KTH Royal Institute of Technology\\
\url{https://www.linkedin.com/in/carlos-barreto}\\
\href{mailto:carlobar@gmail.com}{carlobar@gmail.com} \\
+46 72 024 6186\\
}

\newcommand{\position}{Senior Researcher for Big Data Processing  }
\newcommand{\place}{Dynatrace }



\begin{document}

\begin{letter}{
}
 
\opening{Dear Hiring Manager,}

I write you to express my interest in the position of \position  at \place.
I am a computer scientist and so far have conducted research mainly in cyber security and electrical engineering. This has been a rewarding experience, because each problem is different and often requires diverse tools, such as machine learning, optimization, and statistics. 
%For this reason, in my career I have developed excellent analytical, troubleshooting, and communication skills. 
%
%Currently I am looking for opportunities to use my skills and expertise to do meaningful research, and joining \place \ would be a unique opportunity to me.
%
%
%I have been particularly interested in cyber insurance 
%My interest in the insurance industry started when I got exposed to the elegant maths behind it. Since then I have been involved in related research projects, but I still want to learn how the insurance industry works in practice. For this reason joining \place \ would be a unique opportunity for me.
I would like to keep developing my analytical skills and contribute with the strategic decisions in a business, and I think \place \ would be a great place to do this.




I have PhD degree in Computer Science 
%and a Master degree in Electrical Engineering (with emphasis in control systems) 
and have strong competencies in algorithms, machine learning, statistics, and project management. My expertise in these fields has been developed (beyond coursework) through diverse research projects. 
For example, I have used stochastic dynamic programming to find the optimal strategies to manage cyber risks. 
Also, I have investigated cyber attacks that induce errors on ML-based demand forecasters to manipulate prices in electricity markets. 
%In my latest projects I have worked on diverse problems concerning cyber insurance markets, in particular, mechanisms to address some barriers that hinder the growth of this industry. 

%I am aware of my lack of professional experience outside the academia. However, 
I believe that my experience formulating and executing research projects is relevant for this position. In my previous projects my duties have included: formulate problems, plan activities, configure systems, collect and validate data, automate processes, apply mathematical models and algorithms to test hypothesis, analyze and evaluate results,  and communicate findings to diverse audiences. In addition, some projects also involve collaborating with experts and mentoring students, which often requires being receptive to feedback and patience to manage conflicts.


While my coding background is primarily on Python, I am eager to learn new programming languages and other technologies to broaden my technical skill set. 
%I am very passionate about Linux and have experience using it daily for my personal use and also for my professional work. 
I am confident that my ability to learn and adapt will help me to overcome quickly my lack of experience in other fields.


In closing, 
I believe that this position would be an excellent fit for my background and I am confident that you can find my skills, knowledge, and motivation to learn valuable.

I am looking forward to hearing from you.


\closing{Sincerely,}



\end{letter}
\end{document}

Short version

I am a computer scientist and have conducted research in cyber security and cyber insurance. My interest in the insurance industry started when I got exposed to the elegant maths behind it. Since then I have worked on problems concerning cyber insurance markets, such as mechanisms to address barriers that hinder the growth of this industry. I still want to learn more about the insurance industry, and joining your company would be a unique opportunity for me. 

I have PhD degree in Computer Science and have strong competencies in algorithms, machine learning, and statistics. I believe that my experience formulating and executing research projects is relevant for this position. Some of my duties have included: formulate problems, collect and validate data, use mathematical models and algorithms to test hypothesis, and communicate with diverse audiences. 

